### 2014-06-28 alex/albania.Rmd

Albania is awesome
=============
```{r load, echo=FALSE, results='hide', warning = FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
setwd("..")
sets <- c("school", "student")

@@

scores.df$CNT = factor(scores.df$CNT, levels = scores.df$CNT[order(scores.df$math_difference)])
qplot(CNT, math_difference, data = scores.df, color = OECD, size = OECD) + coord_flip() +
  scale_y_continuous("math score gap: male - female scores", breaks=seq(-30, 30, 5)) +
  geom_hline(yintercept=0, colour="grey80") + scale_size_manual(values = c(4, 2.5, 2.5)) + xlab("")

scores.df$CNT = factor(scores.df$CNT, levels = scores.df$CNT[order(scores.df$read_difference)])
qplot(CNT, read_difference, data = scores.df, color = OECD, size = OECD) + coord_flip() +
  scale_y_continuous("read score gap: male - female scores") +
  geom_hline(yintercept=0, colour="grey80") + scale_size_manual(values = c(4, 2.5, 2.5)) + xlab("")

@@

```{r another idea}
.width = 1

@@

ggplot(mapping = aes(x = OUTHOURS)) + 
  geom_histogram(
    mapping = aes(y = ..density.., fill = OECD), 
    binwidth = .width,
    data = data_small %>% filter(OECD == "Albania")
  ) + 
  geom_line(
    mapping = aes(group = CNT, color = OECD), 
    stat = "density", 
    alpha = 0.3,
    data = data_small %>% filter(OECD != "Albania")
  ) 
```

>>>>

Albania
=============
```{r load, echo=FALSE, results='hide', warning = FALSE, message=FALSE}
library(ggplot2)
library(dplyr)
setwd("..")
sets <- c("school", "student")

@@

scores.df$CNT = factor(scores.df$CNT, levels = scores.df$CNT[order(scores.df$math_difference)])
scores.df$OECD = factor(scores.df$OECD, levels = scores.df$OECD[])

qplot(CNT, math_difference, data = scores.df, color = OECD, size = OECD) + coord_flip() +
  scale_y_continuous("math score gap: male - female scores", breaks=seq(-30, 30, 5)) +
  geom_hline(yintercept=0, colour="grey80") + scale_size_manual(values = c(4, 2.5, 2.5)) + xlab("") +  
  scale_colour_manual(values = c("#ca0020", "#f4a582", "#92c5de"))

scores.df$CNT = factor(scores.df$CNT, levels = scores.df$CNT[order(scores.df$read_difference)])
qplot(CNT, read_difference, data = scores.df, color = OECD, size = OECD) + coord_flip() +
  scale_y_continuous("read score gap: male - female scores") +
  geom_hline(yintercept=0, colour="grey80") + scale_size_manual(values = c(4, 2.5, 2.5)) + xlab("") +  
  scale_colour_manual(values = c("#ca0020", "#f4a582", "#92c5de"))

@@

```{r another idea, fig.width=8, warning = FALSE, message=FALSE}
.width = 1

@@

ggplot(mapping = aes(x = OUTHOURS)) + 
  scale_x_continuous(name = "out of school study time (hours)", limits = c(0,60)) +
  scale_y_continuous(name = "density") +
  geom_histogram(
    mapping = aes(y = ..density.., fill = OECD), 
    binwidth = .width,
    data = data_small %>% filter(OECD == "Albania")
  ) + 
  scale_fill_manual(
    values = "black",
    breaks = "Albania",
    guide = guide_legend(title = "")
  ) + 
  geom_line(
    mapping = aes(group = CNT, color = OECD), 
    stat = "density", 
    alpha = 0.3,
    data = data_small %>% filter(OECD != "Albania")
  ) +
  scale_color_discrete(
    guide = guide_legend(
      title = "Other Countries",
      override.aes = list(alpha = 1)
    )

  ) +
  scale_colour_manual(values = c("#f4a582", "#92c5de")) + guides(colour = guide_legend(override.aes = list(alpha = 1)))
```

### 2014-06-28 dicook/school_matters.Rmd

```{r shortages2}
library(ggplot2)
df2 = df%>% select(CNT, SCHOOLID, mmath, mread, msci, SC14Q02,
                  SC14Q07, SC14Q08, SC14Q09, SC14Q10, SC14Q11,
                  SC14Q12, SC14Q13)
for(i in 6:13) {
  df2[,i] = as.numeric(df2[,i])
}

>>>>

```{r shortages2, eval=FALSE}
library(ggplot2)
df2 = df%>% select(CNT, SCHOOLID, mmath, mread, msci, SC14Q02,
                  SC14Q07, SC14Q08, SC14Q09, SC14Q10, SC14Q11,
                  SC14Q12, SC14Q13)
for(i in 6:13) {
  df2[,i] = as.numeric(df2[,i])
}
